\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty \versionline{2}

### 2015-08-26 ICRA2016/bandits_docs/includes/introduction.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\section{Introduction}
Robots in warehousing and small- to medium-scale manufacturing must be able to efficiently handle to new products and parts.
For example, a robot processing orders in a distribution warehouse must be able to quickly adapt to new consumer products to place them in shipping containers.
Analytic methods for grasp planning requires precise knowledge of contact locations and surface normals,
but a robot in the field may not measure these quantities exactly due to sensor imprecision and missing data resulting from occlusions or highly reflective surfaces.
This motivates a fast and adaptive approach to grasp planning that is robust to uncertainty about the state of the robot and environment.

\TODO{I think the parts about force closure should be greatly compressed here}
Force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}, is a commonly-used binary metric of grasp quality.
Past work has measured the probability of force closure given uncertainty in robot state~\cite{brook2011collaborative, hsiao2011bayesian}, object pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose}, and object shape~\cite{brook2011collaborative, hsiao2011bayesian, kehoe2012estimating, mahler2015gp}.
Computing the probability of force closure requires integrating over the uncertain quantities, which many works have computed using computationally expensive Monte-Carlo integration over sampled perturbations~\cite{christopoulos2007handling, hsiao2011bayesian, kehoe2012toward, kim2012physically, weisz2012pose} parallelized in the cloud~\cite{kehoe2012toward} or using iterative pruning of grasps with low quality~\cite{kehoe2012estimating, kehoe2015survey}.

Recently, Laskey et al.~\cite{laskey2015bandits} showed that it was possible to jointly compute the integral and identify the best grasp using Multi-Armed Bandit (MAB) algorithms such as Thompson Sampling, leading to $5-10\times$ speedups over previous work on a set of parallel-jaw grasps on 2D objects.
However, the MAB algorithms still needed roughly 5,000 samples to identify the best grasp from a pool of 1,000 candidates for each object, which could be time-consuming for 3D objects.
Also, the number of samples is prohibitively high to use the algorithms based on physical success from robot trials instead of in simulation.
One possible reason for the magnitude of samples is that this work treated each grasp and object independently, when in reality grasps and objects with similar features, such as those illustrated in\figref{teaser}, should convey information about the probability of success of one another.

\TODO{Need to get correct terminology. Technically not contextual or combinatorial. Ask Kevin.}
Correlated Multi-Armed Bandits (CMABs) are an extension of standard MABs in which options have correlated rewards.
On each observation, standard MAB algorithms update only the predictive model for the option chosen, while CMAB algorithms typically update a global predictive model of the reward for each option.
This can lead to faster convergence if the algorithm has some knowledge of the correlation structure between options.~\cite{}.
A primary challenge is thus estimating a model of the global correlation structure of the arms, which may require a large amount of data.

In this work, we leverage CMABs to accelerate identification of robust grasps using a correlation structure learned from large amounts of data.
We model the probability of force closure for grasps on 3D shapes as a Correlated Continuous Beta Processes (CCBPs)~\cite{}, a model of 0-1 correlated options with computationally inexpensive posterior updates compared to alternative models such as Gaussian Processes~\cite{}.
Each option corresponds to a single grasp center and axis.
Evaluating an option corresponds to sampling from Gaussian uncertainty in object pose, gripper pose, and contact friction, and measuring force closure for the grasp on the sampled state.
We learn the correlation structure between grasps \TODO{Write up}

Our primary contribution is \TODO{Write up}.
Our experiments show that \TODO{Write up}.

>>>>

\section{Introduction}
\seclabel{introduction}

Robots in warehouse order fullfillment and small- to medium-scale manufacturing must be able to efficiently grasp and manipulate new products and parts.
For example, a robot processing orders in a distribution warehouse must quickly plan graps for new consumer products to place them in shipping containers. 
% Above motivates speed and adaptivity
% Statement motivating robustness to uncertainty
Furthermore, a robot may not fully observe the state of the workspace, such as the pose or frictional properties of consumer products, due to sensor imprecision and missing data resulting from occlusions.
This poses a challenge for grasp planning with either analytic methods~\cite{ferrari1992, ciocarlie2009} that require precise knowledge of contact locations and surface normals or data-driven approaches~\cite{bohg2014data} that attempt to build a statistical model of grasp success over the massive number of configurations of the environment.
%This motivates an approach to grasp planning that is fast, robust to uncertainty about the state of the robot and environment, and can adapt to new objects and perturbations in the envrionment.

Past work has attempted to overcome this by planning grasps analytically with high probability of force closure~\cite{kehoe2012toward, kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose}, or using data-driven methods to predict grasp success from human labels~\cite{balasubramanian2012physical, detry2013learning,  herzog2014learning, kappler2015leveraging, lenz2015deep, saxena2008robotic} or empirical successes on a physical robot~\cite{boularias2014efficient, brook2011collaborative, detry2011learning, kroemer2010combining, montesano2012active}.
Many works on grasp selection with probablity of force closure evaluate a set of candidate grasps using sampling and select the highest quality grasp either using brute force sampling~\cite{kehoe2012toward, kim2012physically, weisz2012pose}, iterative pruning~\cite{kehoe2012estimating}, or Multi-Armed Bandit (MAB) algorithms to adaptively sample more promising grasps~\cite{barto1998reinforcement,
lai1985asymptotically, laskey2015bandits, robbins1985some}.
However, MAB algorithms, the current fastest sampling method, still required approximately 10 samples per grasp to converge to a solution and needed to be re-run for every new object.

On the other hand, data-driven approaches have shown promise over analytic methods on physical robot trials~\cite{balasubramanian2012physical, herzog2014learning} possibly due to a reduction in modelling error.
The number of objects and grasps tested is typically on the order of tens to hundreds for physical robot trials and at most a few thousand objects and hundreds of thousands of grasps when using simulation or human labels~\cite{goldfeder2009columbia, lenz2015deep, kappler2015leveraging}.
In comparison, state-of-the-art learning results in image classification~\cite{deng2009imagenet, krizhevsky2012imagenet} and speech recognition~\cite{cieri2004fisher, hannun2014deepspeech} relied on datasets containing tens of millions of examples.
This raises the question: will maching learning for grasp planning under vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
%may require orders of magnitude more data than in use currently.

%This motivated gradient-based methods based on approximations to the probabliity of force closure~\cite{mahler2015gp} and using Multi-Armed Bandit algorithms to adaptively sample more promising grasps~\cite{laskey2015bandits}, which reduced the number of samples until convregence by 10$\times$.
%However, the number of iterations was still prohibitively high for real-time execution and prior knowledge could not be utilized for new objects.

To make progress toward answering this question, we introduce the Dexterity Network (DexNet) 1.0, a dataset of tens of thousands of 3D mesh models and a system for building statistical models that predict grasp quality across the dataset.
DexNet is composed of laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking}, and synthetic 3D mesh models from 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}.
~\figref{dexnet-teaser} shows a subset of the objects in the dataset.
To measure similarity between objects, we form an object network based on Deep Convolutional Neural Networks (CNNs) trained to predict object categories from synthetic rendered images of each object~\cite{aubry2015understanding, li2015comparison}.
The DexNet system uses Google Compute Engine to launch up to 600 instances at a time to samples and evaluate grasps on subsets of objects and to learn predictive models of grasp quality.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the DexNet dataset. The dataset consists of over 30,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet} and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison} }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

In this work, we use DexNet to study the number of samples that MAB algorithms take to converge to a grasp with high probability of force closure across orders of magnitude of prior data of grasps with known quality.
To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for grasps on similar objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
CCBPs allow us to form a prior belief on the quality of candidate grasps for a new object based on data in DexNet and to efficiently update a global belief on the quality of all candidate grasps on an object after observing the outcome of a single sampled grasp.
We measure local similarities between grasps on the same object by a distance between the gripper poses and the similarity between local surface patches near the mean location of contact on the object~\cite{herzog2014learning, kappler2015leveraging}.
We measure global similarity in shape based on the distance between the objects in DexNet.
Our results suggest \TODO{Fill in with new results}.
%While we acknowledge probability of force closure has shortcomings~\cite{balasubramanian2012physical}, we use it in this work because it is relatively inexpensive to evaluate computationally, allowing us to better examine the effects of scale.

### 2015-08-26 ICRA2016/bandits_docs/includes/problem_statement.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.

We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}. 
%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

We measure grasp quality by the probability of force closure subject to these uncertain quantities.
Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
Then the probability of force closure for a grasp $\bg$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$

\vspace{-2ex}
\begin{align}
	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
\end{align}

\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}

Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

>>>>

We consider the problem of finding the parallel-jaw grasp with the maximum probability of a binary success metricsuch as force closure on a previously unknown object under uncertainty in object pose, gripper pose, and friction coefficient.

\subsection{Grasp and Object Model}
Our grasping model is illustrated in~\figref{grasp-model}.
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \mS^2$.
We assume that the gripper will be opened to its maximal width before closing on the object.
Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{newcombe2011kinectfusion, mahler2015gp}, which is zero on the object surface, positive outside the object, and zero inside the object. 
We assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \mS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
Our joint grasp and object space, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.png}
\caption{(Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \mS^2$. The grasp parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame located at the object center of mass $\bz$ and oriented along the principal directions of the object. (Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \mathbb{S}^2$. The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$. From these parameters we can derive the theoretical forces and torques that the gripper can apply to the object. }
\figlabel{grasp-model}
\vspace*{-15pt}
\end{figure}

%Let $\mM = \left\{\mV, \mT \right\}$ be a triangular mesh representing an object's geometry, where $\mV = \{\bw_i \in \mathbb{R}^3 \}_{i=1}^{N_v}$ is a set of $N_v$ vertices and $\mT = \{ \bt_i \in \mathbb{Z}_{+}^3 \}_{i=1}^{N_t}$ is a set of $N_t$ triangles formed by triplets of integer indices of vertices.
%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.

\subsection{Sources of Uncertainty}
We assume known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}.
%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ be Gaussian uncertainty in object pose with mean $\bar{T} \in SE(3)$ and covariance $\Sigma_{\xi}$ following the model of Barfoot and Furgale~\cite{barfoot2014associating}.
Let $\nu$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\nu} \in \mG$ and covariance $\Sigma_{\nu}$.
Let $\gamma$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\gamma} \in \mathbb{R}$ and covariance $\Sigma_{\gamma}$.
Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.

\subsection{Contact Model}
Our contact model is illustrated in the right panel of \figref{grasp-model}.
Given object shape and samples of object pose, and gripper pose, we let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
Furthermore, let $\bn_i \in \mS^2$ denote the surface normal at contact $\bc_i$.
To compute the forces that each contact can apply to the object, we discretize the friction cone at contact $i$ into a discrete set of $N_c$ facets with vertices $\bbf_{i,j}$ for $j = 1, ..., N_c$~\cite{pokorny2013classical} for a given friction coefficient $\gamma$.
Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
Thus the set of all wrenches that can be applied by a grasp $\bg$ is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., N_c\}$.

\subsection{Quality Metric}
In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{} and that some evidence suggests that deterministic force closure is not a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
However, we use the probability of force closure because of it has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate as compared to human labels or physical executions, allowing us to better study the effects of large amounts of data on convergence.

Let $F \in \{0, 1\}$ denote the occurence of force clsoure.
To compute force closure for a grasp $\bg$ on object $\mO$ given deterministic samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.5]{figures/illustrations/dexnet_graphical_model_simple.png}
\caption{A graphical model describing the relationships between known uncertain parameters (shaded gray) such as object pose and the force closure random variable $F$.}
\figlabel{graphical-model}
\vspace*{-15pt}
\end{figure}

\subsection{Objective}
The probability of force closure for a grasp $\bg$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \rho, \zeta \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$:

\vspace{-2ex}
\begin{align}
	\underset{g_{I(1)}, ..., g_{I(T)} \in \mG}{\text{maximize }} \sum \limits_{t=1}^T P_F(g_{I(t)}). \label{eq:objective}
\end{align}

As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
However, even with a discrete set of candidates, fully evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}

### 2015-08-26 ICRA2016/bandits_docs/includes/related_work.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{laskey2015bandits}.
In reality, grasp correlations may occur from grasps with similar configurations~\cite{ciocarlie2009, detry2011learning}, objects with similar global structure~\cite{pokorny2013grasp}, or on point cloud surfaces with similar local geometry~\cite{boularias2011learning, herzog2012template, kroemer2010combining, saxena2008robotic}.
Correlated Multi-Armed Bandit (CMAB) models, sometimes also referred to as Bayesian Optimization models~\cite{brochu2010tutorial}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{chu2011contextual} and envrionmental monitoring in robotics~\cite{hitz2014fully, marchant2012bayesian}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{chu2011contextual}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{rasmussen2006}, which can model nonlinear relationships between options and rewards.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypothesse via imitation learning and Gaussian process upper-confidence bounds to predict grasp successeses and determine the next grasp to select.
Boularias et al.~\cite{boularias2014efficient} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks. 
However, GP models are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far)~\cite{rasmussen2006}, which limited the scale of experiments in both simulation and the physical world that the authors could perform.
To make the model more tractable, Boularias et al. later extended their work to use an heuristic upper confidence bound-based reinforcement learning~\cite{boularias2015learning}.
Recently, Goetschalckx et al.~\cite{goetschalckx2011continuous} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{goetschalckx2011continuous}.
Montesano and Lopes~\cite{montesano2012active} used CCBPs (although the authors did not refer to them as CCBPs) to actively acquire grasp executions, measuring correlations from the responses to a bank of 151 image filters.
In this work we also utilize CCBPs to model correaltions between grasps, and study their performance on grasping simulations over thousands of objects.

>>>>

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{laskey2015bandits}.
In reality, grasp correlations may occur from grasps with similar configurations~\cite{ciocarlie2009, detry2011learning}, objects with similar global structure~\cite{pokorny2013grasp}, or on point cloud surfaces with similar local geometry~\cite{boularias2011learning, herzog2012template, kroemer2010combining, saxena2008robotic}.
Correlated Multi-Armed Bandit (CMAB) models, sometimes also referred to as Bayesian Optimization models~\cite{brochu2010tutorial}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{chu2011contextual} and envrionmental monitoring in robotics~\cite{hitz2014fully, marchant2012bayesian}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{chu2011contextual}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{rasmussen2006}, which can model nonlinear relationships between options and rewards.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypothesse via imitation learning and Gaussian process upper-confidence bounds to predict grasp successeses and determine the next grasp to select.
Boularias et al.~\cite{boularias2014efficient} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks. 
However, GP models are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far)~\cite{rasmussen2006}, which limited the scale of experiments in both simulation and the physical world that the authors could perform.
To make the model more tractable, Boularias et al. later extended their work to use an heuristic upper confidence bound-based reinforcement learning~\cite{boularias2015learning}.
Recently, Goetschalckx et al.~\cite{goetschalckx2011continuous} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when approximate kernels are computed using efficient nearest neighbor queries~\cite{goetschalckx2011continuous}.
Montesano and Lopes~\cite{montesano2012active} used CCBPs (although the authors did not refer to them as CCBPs) to actively acquire grasp executions, measuring correlations from the responses to a bank of 151 image filters.
In this work we also utilize CCBPs to model correaltions between grasps, and study their performance on grasping simulations over thousands of objects.

### 2015-08-26 ICRA2016/bandits_docs/paper.tex
Added initial intro and related work. Pretty rough and bibtex not yet updated
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\begin{document}
\title{\LARGE \bf Continuous Correlated Beta Processes for 3D Grasp Planning Under Uncertainty
	\versionline{1}}
\author{Jeffrey Mahler, Brian Hou, Michael Laskey, ..., Pieter Abbeel, Ken Goldberg}
%\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
%\{jmahler, zmccarthy, sachinpatil, pabbeel, goldberg\}@berkeley.edu} 
\maketitle

%\input{includes/abstract}
%
%\input{includes/introduction}
%\input{includes/relatedwork}
%
\input{includes/problem_statement}
\input{includes/background}
%\input{includes/methodology}
%\input{includes/analysis}
%\input{includes/experiments}
%\input{includes/conclusion}

>>>>

\begin{document}
\title{\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{2}}
\author{Jeffrey Mahler, Brian Hou, Mel Roderick, Michael Laskey, Kai Kohlhoff, \\ Torsten Kroeger, Florian Pokorny, James Kuffner, Ken Goldberg}
%\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
%\{jmahler, zmccarthy, sachinpatil, pabbeel, goldberg\}@berkeley.edu} 
\maketitle

\TODO{Possibly will include Matthieu Aubry and Pieter Abbeel as coauthors as well}

\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/background}
\input{includes/algorithm}
%\input{includes/analysis}
\input{includes/experiments}
%\input{includes/conclusion}
